\section{RDF-Kernels}
\subsection{Motivation}
\begin{frame}[fragile,t]
\frametitle{Combining RDF with Machine learing}
\begin{block}{Goal}
We want to apply Machine learning algorithms on RDF.
\end{block}
\pause
\begin{comment}
\begin{center}

\begin{tikzpicture}
  \draw[thick,rounded corners=1pt] (1,2.5) -- (3,3);
  \draw[thick,rounded corners=1pt] (1,1) -- (3,3);
  \draw[thick,rounded corners=1pt] (3,1) -- (3,3);
  \draw[thick,rounded corners=1pt] (3,1) -- (1,1);
  \draw[thick,rounded corners=1pt] (1,2.5) -- (0,1.5);
  \draw[thick,rounded corners=1pt] (1,2.5) -- (3,3);
  \draw[thick,rounded corners=1pt] (1,1) -- (0,1.5);
  \draw[fill=gray] (1,2.5) circle (0.25cm);
  \draw[fill=gray] (3,3) circle (0.25cm);
  \draw[fill=gray] (1,1) circle (0.25cm);
  \draw[fill=gray] (3,1) circle (0.25cm);
  \draw[fill=gray] (0,1.5) circle (0.25cm);
  \end{tikzpicture}

\end{center}
\end{comment}
\begin{itemize}
\item Rescource Description Frameworks (RDF) impose a Graph structure on the Data \pause
\item Machine learning algorithms are optimzed on certain Data Structures (Tables etc.)
\end{itemize}
\textbf{Problem!}
\pause
\\
\textbf{Solutions}:
\begin{enumerate}
\item Rewrite the ML-Algorithms for RDF Data
\item Try to transform the RDF Data that it suits ML-Algorithms
\end{enumerate}

\end{frame}
\begin{frame}[fragile,t]
\frametitle{Kernels mathematically}
\begin{comment}
We want to consider a certain class of Machine learing Algorithms: Kernel based ones.
\end{comment}


\begin{comment}
\begin{itemize}

\item ... summarize Data-pairs as a single scalar value $K(d,d)\in \mathbb{R}$
\pause
\item ... can be used to embed Data in higher-spaced rooms.
\pause
\item ... can be used directly for machine-learning concepts like NNS, some NN, SVMs.
\pause
\end{itemize}
\end{comment}
\begin{block}{Definition}
Let $D$ be the Space of Data, $\psi: D \rightarrow F$ a mapping representing the Data as $F \subset \mathbb{R}^n$. A function K with a represenation \\

\[ K: D \times  D  \rightarrow \ \mathbb{R}\]
\[ K(d_1,d_2)\ =\ <\psi(d_1),\psi(d_2)> \]
is called Kernel.
\end{block}

Short version: 
\begin{enumerate}
\item We take our Data $d_1$, $d_2$
\item We transfer them to real-valued vectors $\psi(d_1),\psi(d_2)$
\item We apply a scalar product.
\end{enumerate}

\end{frame}


\subsection{Kernels for RDF}
\begin{frame}[fragile, t]
\frametitle{Kernels for RDF}
Let $G = (s,p,o)$ be our RDF. \\
\pause
What is D ?
\begin{itemize} \pause
\item $D = \{G', G' \subset G\}$
\end{itemize}
What Kernels can we define for Graphs? \pause
\vspace{5pt}
Lösch et al. proposed for different suitable kernels.
\begin{enumerate}
\item Walk Kernel
\item Path Kernel
\item Full Subtree Kernel
\item Partial Subtree Kernel
\end{enumerate}
\end{frame}

\begin{frame}[fragile, t]
\frametitle{Example: The path kernel}
\begin{center}
\begin{tikzpicture}
  \draw[thick,rounded corners=1pt] (1,1) -- (3,2.5);
  \draw[thick,rounded corners=1pt] (3,1) -- (3,2.5);
  \draw[thick,rounded corners=1pt] (3,1) -- (1,1);
  \draw[thick,rounded corners=1pt] (1,2.5) -- (0,1.5);
  \draw[thick,rounded corners=1pt] (1,2.5) -- (3,2.5);
  \draw[thick,rounded corners=1pt] (1,1) -- (0,1.5);
  \draw[thick,rounded corners=1pt] (3,2.5) -- (4,2.5);
  \draw[thick,rounded corners=1pt] (4,2.5) -- (2,4);
  \draw[thick,rounded corners=1pt] (4,2.5) -- (3,1);
  \draw[thick,rounded corners=1pt] (2,4) -- (1,2.5);
  \draw[fill=gray] (1,2.5) circle (0.25cm);
  \draw[fill=purple] (3,2.5) circle (0.25cm);
  \draw[fill=purple] (1,1) circle (0.25cm);
  \draw[fill=purple] (3,1) circle (0.25cm);
  \draw[fill=blue] (4,2.5) circle (0.25cm);
  \draw[fill=gray] (2,4) circle (0.25cm);
  \draw[fill=red] (0,1.5) circle (0.25cm);
  \end{tikzpicture}
\end{center}
\[\kappa_{l,\lambda}=\sum_{i=1}^l \lambda^i |\{p | p \in paths_i(G_1 \cap G_2) \} \]
\end{frame}


\subsection{Relevance}
\begin{frame}[fragile, t]
\frametitle{Example}
Why this approach ? \vspace{5pt}
\pause
Lösch U., Bloehdorn, S., Rettinger, A. showed that this approach of applying Graph Kernels to RDF show almost the same peformance as retailoring ML algorithms to RDF structure.
\end{frame}
\section{Implementation}

\subsection{General Concept}
\begin{frame}[fragile,t]
\frametitle{Concept}
\begin{itemize}
\item Build an Interface for the mangement of kernel information / values. 
\begin{itemize}
\pause
\item Give the possibility to use User defined Update/Deletation algorithms and kernels.
\pause 
\item Provide the defined example Kernels with efficient implementation of Update/Deletation

\end{itemize}
\end{itemize}
\end{frame}

\subsection{Ideas for Implementation}
\begin{frame}[fragile,t]
\frametitle{Computation of Predefined Kernels}
\begin{itemize}
\item Use Sansa's Graph Querying for Calculation of Trees, Paths.
\pause
\item[+] Faster than Sparks RDD querying. 
\pause
\item[+] Computational Performance will scale up with SANSA's performance.
\end{itemize}
\end{frame}

\begin{frame}[fragile,t]
\frametitle{Value Storage}
Two ideas:
\pause
\begin{enumerate}
\item Store Kernel-Values directly in original RDF
\begin{itemize}
	\item [+] All information is provied in Consistent Format.
	\item [+] Induces a Distance Graph on Original RDF.
	\item [+] Can be used for further analysis outside of Sansa
	\pause
	\item [-] Do we really want to store everything permanently in the Dataset ?
	\item [-] ML-Algorithms need a lot of quering for extraction of Kernel Values.
\end{itemize}
\pause
\item Store Kernel-Values in seperate Structure.
\begin{itemize}
	\item [+] No Changes on original RDF.
	\item [+] Only relevant Information for ML/DM. 
	\pause
	\item [-] What size ? (Has to be Scalable, e.g updates )
	\item [-] What structure ?  (f.e Distance Matrix: Inefficient if Sparse)
	\item [-] Has to be a know format ! Otherwise not user friendly.
\end{itemize}
\end{enumerate}
\end{frame}

\begin{frame}[fragile,t]
\frametitle{new Idea}
\begin{itemize}
\item Use an RDF for storing the Kernel values. \pause
\item Offer both possiblities:
\begin{enumerate}
\item Store Kernels in original RDF
\item Store Kernels in seperate reduced RDF (Original RDF without any Predicates and Attributes, except Kernel Oriented information)
\end{enumerate}
\pause
\item[+] Same implementation for both variants. Only different target for saving the values
\item[+] User can pick which one he favours.
\item[+] In each way the user is familiar with the storage format.
\item[+] A posteriori the RDFs can still be merged.
\end{itemize}
\end{frame}










